### 2016-04-28 ch06-concl/conclusions.tex
Comments Tom: conclusion

  \subsection{Excitation design}
  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
  Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
  As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid with frequency resolution $\Delta f$ should conform to
  \begin{equation}
    \alpha \leq 1 + \damping[\min]
  \end{equation}
  to attain a reliable estimate of the resonances present in the system.
  The choice to use the equality $\alpha = 1+ \damping[\min]$ is the optimal choice within the framework presented in \chapref{sec:excitation} such that resonances with $\damping \geq \damping[\min]$ and $\wn \geq \omegaLinLog = \frac{2 \pi \Delta f}{\alpha-1} = \frac{2 \pi \Delta f}{\damping[\min]}$ are well-represented in the \gls{FRF}.
  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited.

@@

  \subsection{Non-parametric estimation}
  Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
  It has been shown that the most general \gls{LRIC} is very sensitive to the use of the `correct' local model order.
  The pre-existing \gls{LRM} and \gls{LPM}, however, are not as sensitive.
  It has been shown that the inherent bias of the \gls{LRM} becomes the dominant source of errors, in contrast to the variance, when an \gls{SNR} of less than $20\unit{dB}$ is available in the frequency bands of interest.
  For resonant systems, the \gls{LRM} is superior to the \gls{LPM} in terms of both bias and \gls{RMS} error in almost all cases.
  The \gls{LPM} is slightly superior for very noisy datasets ($\SNR < 20 \unit{dB}$) that have a very limited frequency resolution.

@@

  \subsection{Initialization of parametric estimation}
  To obtain a parametric model estimate from measured data often requires solving a non-convex optimization problem.
  However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers, in particular for cases where a low \gls{SNR} is available yet a lot of measurements are available.
  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM} and \gls{RFIR}.
  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
  These smoothers allow one to obtain good models from noisier data than what existing techniques.
  The improvement of the initial values has been verified both on simulations, measurements and a simulation stress test consisting of different filters.
  While overall the \gls{RFIR} provides the best starting values from the different smoothers, combining multiple initial values remains a very valuable approach to make a system identification toolbox robust for the measurement data.

\section{Future Perspectives}
  \subsection{Excitation Design}
  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time~\citep[Section 2.7]{Pintelon2012}:
  \begin{itemize}
    \item Zippered multisines, where the frequency grids of the different input channels are interspersed. This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
    \item Orthogonal multisines, which are computationally more involved to process, require multiple experiments but allow for finer frequency resolution.
  \end{itemize}
  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.

@@

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp ji\dW\Ts)}{\Sum_i  a_i \exp ji\dW\Ts }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.

@@

    In particular, for slowly time-varying systems, windows can be used in combination with the \gls{STFT} to obtain a rough approximation of either the output spectrum or the transfer characteristic of (slowly) time-varying systems.
    In this context, the \gls{LPM} has already been used~\citep{Lataire2012}.
    Preliminary tests using the \gls{LRM} in lieu of the \gls{LPM} have proven fruitful.
    Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep[Chapter 4]{vanderMaas2016PhD}.
    Given these successes of \gls{LRM} to estimate a preliminary model of both parameter-varying and time-varying models in more complicated experimental settings.
    E.g. it could prove useful to extend the \gls{LRM} towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.

@@

  \subsection{Non-parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, a major objective for future research is to extend the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds needs to be made more explicit and verified experimentally.

  Another possibility for future research is approach the problem of $\Hinf$ gain estimation purely form the aspect of local regression such that combining multiple models is no longer necessary.

@@

As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
There are a few approaches that we think are worthwhile to investigate.
On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
On the other hand, one could devise crude model order selection procedures, e.g.  estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
This doesn't do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.

>>>>

\section{Results of this Research}
\TODO{general introduction, claim the title, reaffirm the structure of the book}

  \subsection{Excitation Design}
  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
  Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
  As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed (relative) uncertainty of the identified \gls{FRF} near the resonance peaks as caused by the measurement noise.
  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid with frequency resolution $\Delta f$ should conform to
  \begin{equation}
    \alpha \leq 1 + \damping[\min]
  \end{equation}
  to attain a reliable estimate of the resonances present in the system.
  The choice to use the equality $\alpha = 1+ \damping[\min]$ is the optimal choice within the framework presented in \chapref{sec:excitation} such that resonances with $\damping \geq \damping[\min]$ and $\wn \geq \omegaLinLog = \frac{2 \pi \Delta f}{\alpha-1} = \frac{2 \pi \Delta f}{\damping[\min]}$ are well-represented in the \gls{FRF}.
  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited.

@@

  \subsection{Non-parametric Estimation}
  Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
  It has been shown that the most general \gls{LRIC} is very sensitive to the use of the `correct' local model order.
  The pre-existing \gls{LRM} and \gls{LPM}, however, are not as sensitive.
  It has been shown that the inherent bias of the \gls{LRM} becomes the dominant source of errors, in contrast to the variance, when an \gls{SNR} of less than $20\unit{dB}$ is available in the frequency bands of interest.
  For resonant systems, the \gls{LRM} is superior to the \gls{LPM} in terms of both bias and \gls{RMS} error in almost all cases.
  The \gls{LPM} is slightly superior for very noisy datasets ($\SNR < 20 \unit{dB}$) that have a very limited frequency resolution.

@@

  \subsection{Initialization of Parametric Estimation}
  To obtain a parametric model estimate from measured data often requires solving a non-convex optimization problem.
  However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers, in particular for cases where a low \gls{SNR} is available yet a lot of measurements are available.
  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM} and \gls{RFIR}.
  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
  These smoothers allow one to obtain good models from noisier data than what existing techniques.
  The improvement of the initial values has been verified both on simulations, measurements and a simulation stress test consisting of different filters.
  While overall the \gls{RFIR} provides the best starting values from the different smoothers, combining multiple initial values remains a very valuable approach to make a system identification toolbox robust for the measurement data.

\section{Future Perspectives}
  \subsection{Excitation Design}
  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time~\citep[Section 2.7]{Pintelon2012}:
  \begin{itemize}
    \item Zippered multisines, where the frequency grids of the different input channels are interspersed. This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
    \item Orthogonal multisines, which are computationally more involved to process, require multiple experiments but allow for finer frequency resolution.
  \end{itemize}
  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
  The use of \gls{LRM}/\gls{LPM} may help to overcome that the frequency grids for the different input/output channels do not coincide for zippered signals.

@@

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp (ji\dW\Ts)}{\Sum_i  a_i \exp (ji\dW\Ts) }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.

@@

    In particular, for slowly time-varying systems, windows can be used in combination with the \gls{STFT} to obtain a rough approximation of either the output spectrum or the transfer characteristic of (slowly) time-varying systems.
    In this context, the \gls{LPM} has already been used~\citep{Lataire2012}.
    Preliminary tests using the \gls{LRM} in lieu of the \gls{LPM} have proven fruitful.
    Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep{vanderMaas2015CDC}.
    Given these successes of \gls{LRM} to estimate a preliminary model of both parameter-varying and time-varying models in more complicated experimental settings.
    E.g. it could prove useful to extend the \gls{LRM} towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.

@@

  \subsection{Non-parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.

  Another possibility for future research is to approach the problem of $\Hinf$ gain estimation purely from the aspect of local regression such that combining multiple local models is no longer necessary.

@@

As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
There are a few approaches that we think are worthwhile to investigate.
On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
On the other hand, one could devise crude model order selection procedures, e.g.  estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
This does not do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.
